
---
title: "Evaluate Leave-One-Out State-level Predictions"
output: md_document
---


```{r, results=FALSE, message=FALSE, warning=FALSE}
library(data.table)
library(ggplot2)
library(rpart)
library(irr)
library(Hmisc)
library(printr)
```

#### Load LOO State predictions from train_and_predict notebooks

```{r, warning=FALSE}
q66_prevalence_preds = rbindlist(lapply(
  grep("q66", list.files("~/YRBS_predictions/data/yrbs_20210904", full.names=T), value=T), 
  fread))

q67_prevalence_preds = rbindlist(lapply(
  grep("q67", list.files("~/YRBS_predictions/data/yrbs_20210904", full.names=T), value=T), 
  fread))

q66_male_prevalence_preds = rbindlist(lapply(
  grep("q66", list.files("~/YRBS_predictions/data/yrbs_males_q66_20210904", full.names=T), value=T), 
  fread))

print(nrow(q67_prevalence_preds[year == 2017 & predset == "Using Contact Responses"]))
```


```{r}
# Encode true state-level proportions (2017 YRBS estimates)
q66_true_prevalences = q66_prevalence_preds[year == 2017, .(real_prev = mean(real_prop)),  by=c('pred_state')]
q67_true_prevalences = q67_prevalence_preds[year == 2017, .(real_prev = mean(real_prop)),  by=c('pred_state')]
q66_male_true_prevalences = q66_male_prevalence_preds[year == 2017, .(real_prev = mean(real_prop)),  by=c('pred_state')]
```

#### For each model, prediction dataset, calculate ICC and prediction interval coverage

```{r}
get_eval_stats = function(true_prevalences, prevalence_preds, pred_method, pred_model, pred_predset, pred_year, pred_col) {
  
  subset_dt = prevalence_preds[
    model == pred_model &
    predset == pred_predset &
    year == pred_year
  ]

  pred_prev_by_state = subset_dt[,.(
    pred_state,
    pred_prev = get(pred_col),
    n
  )]

  # add real prevs
  pred_prev_by_state = merge(pred_prev_by_state, true_prevalences, by = 'pred_state')

  # prediction intervals using empirical out-of-bag T distribtion
  pred_prev_by_state = rbindlist(lapply(pred_prev_by_state[, unique(pred_state)], function(s) {

    oob_mean_bias = pred_prev_by_state[pred_state != s, mean(real_prev - pred_prev)]
    #message(paste("oob_mean_bias:", oob_mean_bias))
    oob_sd = pred_prev_by_state[pred_state != s, sd(real_prev - pred_prev)]
    oob_df = pred_prev_by_state[pred_state != s, .N] - 1
    
    real_prev_interval = binconf(pred_prev_by_state[pred_state == s, real_prev*n], 
                                 pred_prev_by_state[pred_state == s, n])

    return(data.table(
      pred_state = s,
      real_prev = pred_prev_by_state[pred_state == s, real_prev],
      real_prev_lb = real_prev_interval[,"Lower"],
      real_prev_ub = real_prev_interval[,"Upper"],
      # T out-of-bag method
      norm_oob_pe = pred_prev_by_state[pred_state == s, pred_prev + oob_mean_bias],
      norm_oob_lb = pred_prev_by_state[pred_state == s, pred_prev + oob_mean_bias - qt(0.975, oob_df)*oob_sd],
      norm_oob_ub = pred_prev_by_state[pred_state == s, pred_prev + oob_mean_bias + qt(0.975, oob_df)*oob_sd]
    ))

  }))

  # add columns to state predictions dt
  pred_prev_by_state[,`:=`(
    pred_method = pred_method,
    pred_model = pred_model
  )]

  # summary result dt
  oob_icc_res = icc(pred_prev_by_state[, .(norm_oob_pe, real_prev)], model = "oneway", type = "agreement", unit = "average")
  summary_dt = data.table(
    pred_method,
    pred_model,
    oob_icc = round(oob_icc_res$value,3),
    oob_icc_pval = round(oob_icc_res$p.value,3),
    oob_coverage = mean(pred_prev_by_state[, norm_oob_lb < real_prev & norm_oob_ub > real_prev])
  )

  return(list(
    state_predictions = pred_prev_by_state,
    summary_stats = summary_dt
  ))
}


# TEST

get_eval_stats(
  true_prevalences = q66_male_true_prevalences,
  prevalence_preds = q66_male_prevalence_preds, 
  pred_method = "Same year with other focal Q",
  pred_model = "rf", 
  pred_predset = "Using Identity Responses",
  pred_year = 2017, 
  pred_col = "pred_prop")$summary_stats
```
#### Inspect LOO RF predictions for each state and prediction dataset

```{r}
MODEL = "rf"

q66_state_preds = rbind(
  get_eval_stats(
    true_prevalences = q66_true_prevalences,
    prevalence_preds = q66_prevalence_preds, 
    pred_method = "Same year with other focal Q",
    pred_model = MODEL, 
    pred_predset = "Using Identity Responses",
    pred_year = 2017, 
    pred_col = "pred_prop")$state_predictions,
  get_eval_stats(
    true_prevalences = q66_true_prevalences,
    prevalence_preds = q66_prevalence_preds, 
    pred_method = "Same year without other focal Q",
    pred_model = MODEL, 
    pred_predset = "Not Using Identity Responses",
    pred_year = 2017, 
    pred_col = "pred_prop")$state_predictions,
  get_eval_stats(
    true_prevalences = q66_true_prevalences,
    prevalence_preds = q66_prevalence_preds, 
    pred_method = "Previous year without other focal Q",
    pred_model = MODEL, 
    pred_predset = "Not Using Identity Responses",
    pred_year = 2015, 
    pred_col = "pred_prop_2017")$state_predictions
)

q66_real_prevs_states = unique(q66_state_preds[pred_method == "Same year without other focal Q", .(pred_state, real_prev, real_prev_lb, real_prev_ub)])
q66_real_prevs_states[, real_txt := paste0(
  format(real_prev*100,digits=0,nsmall=1), " (", 
  format(real_prev_lb*100,digits=0,nsmall=1), ", ", 
  format(real_prev_ub*100,digits=0,nsmall=1), ")")]
q66_real_prevs_states = q66_real_prevs_states[, .(pred_state, real_txt)]
#display(q66_real_prevs_states)

q66_pred_prevs_states = q66_state_preds[, .(pred_state, norm_oob_pe, norm_oob_lb, norm_oob_ub, pred_method)]
q66_pred_prevs_states[, pred_txt := paste0(
  format(norm_oob_pe*100,digits=0,nsmall=1), " (", 
  format(norm_oob_lb*100,digits=0,nsmall=1), ", ", 
  format(norm_oob_ub*100,digits=0,nsmall=1), ")")]
q66_pred_prevs_states_cast = dcast(q66_pred_prevs_states, pred_state ~ pred_method, value.var=c('pred_txt'))
#display(q66_pred_prevs_states_cast)

q66_merged = merge(q66_real_prevs_states, q66_pred_prevs_states_cast, by='pred_state')
q66_merged[is.na(q66_merged)] = ""
q66_merged = q66_merged[,.(
    pred_state, real_txt, `Same year with other focal Q`, `Same year without other focal Q`, `Previous year without other focal Q`
)]
fwrite(unique(q66_state_preds[, .(pred_state, real_prev)]), '~/YRBS_predictions/data/q66_real_prevs.csv')
fwrite(q66_merged, '~/YRBS_predictions/data/q66_merged_preds.csv')
fwrite(merge(q66_pred_prevs_states, unique(q66_state_preds[, .(pred_state, real_prev)]), by='pred_state'), '~/YRBS_predictions/data/q66_raw_preds.csv')
q66_merged
```



```{r}
MODEL = "rf"

q67_state_preds = rbind(
  get_eval_stats(
    true_prevalences = q67_true_prevalences,
    prevalence_preds = q67_prevalence_preds, 
    pred_method = "Same year with other focal Q",
    pred_model = MODEL, 
    pred_predset = "Using Contact Responses",
    pred_year = 2017, 
    pred_col = "pred_prop")$state_predictions,
  get_eval_stats(
    true_prevalences = q67_true_prevalences,
    prevalence_preds = q67_prevalence_preds, 
    pred_method = "Same year without other focal Q",
    pred_model = MODEL, 
    pred_predset = "Not Using Contact Responses",
    pred_year = 2017, 
    pred_col = "pred_prop")$state_predictions,
  get_eval_stats(
    true_prevalences = q67_true_prevalences,
    prevalence_preds = q67_prevalence_preds, 
    pred_method = "Previous year without other focal Q",
    pred_model = MODEL, 
    pred_predset = "Not Using Contact Responses",
    pred_year = 2015, 
    pred_col = "pred_prop_2017")$state_predictions
)

q67_real_prevs_states = q67_state_preds[pred_method == "Same year without other focal Q", .(pred_state, real_prev, real_prev_lb, real_prev_ub)]
q67_real_prevs_states[, real_txt := paste0(
  format(real_prev*100,digits=0,nsmall=1,trim=T), " (", 
  format(real_prev_lb*100,digits=0,nsmall=1,trim=T), ", ", 
  format(real_prev_ub*100,digits=0,nsmall=1,trim=T), ")")]
q67_real_prevs_states = q67_real_prevs_states[, .(pred_state, real_txt)]

q67_pred_prevs_states = q67_state_preds[, .(pred_state, norm_oob_pe, norm_oob_lb, norm_oob_ub, pred_method)]
q67_pred_prevs_states[, pred_txt := paste0(
  format(norm_oob_pe*100,digits=0,nsmall=1,trim=T), " (", 
  format(norm_oob_lb*100,digits=0,nsmall=1,trim=T), ", ", 
  format(norm_oob_ub*100,digits=0,nsmall=1,trim=T), ")")]

q67_pred_prevs_states_cast = dcast(q67_pred_prevs_states, pred_state ~ pred_method, value.var=c('pred_txt'))

q67_merged = merge(q67_real_prevs_states, q67_pred_prevs_states_cast, by='pred_state')
q67_merged[is.na(q67_merged)] = ""
q67_merged = q67_merged[,.(
    pred_state, real_txt, `Same year with other focal Q`, `Same year without other focal Q`, `Previous year without other focal Q`
)]
fwrite(q67_merged, '~/YRBS_predictions/data/q67_merged_preds.csv')
fwrite(merge(q67_pred_prevs_states, unique(q67_state_preds[, .(pred_state, real_prev)]), by='pred_state'), '~/YRBS_predictions/data/q67_raw_preds.csv')
fwrite(unique(q67_state_preds[, .(pred_state, real_prev)]), '~/YRBS_predictions/data/q67_real_prevs.csv')
q67_merged
```


```{r}
MODEL = "rf"

q66_male_state_preds = rbind(
  get_eval_stats(
    true_prevalences = q66_male_true_prevalences,
    prevalence_preds = q66_male_prevalence_preds, 
    pred_method = "Same year with other focal Q",
    pred_model = MODEL, 
    pred_predset = "Using Identity Responses",
    pred_year = 2017, 
    pred_col = "pred_prop")$state_predictions,
  get_eval_stats(
    true_prevalences = q66_male_true_prevalences,
    prevalence_preds = q66_male_prevalence_preds, 
    pred_method = "Same year without other focal Q",
    pred_model = MODEL, 
    pred_predset = "Not Using Identity Responses",
    pred_year = 2017, 
    pred_col = "pred_prop")$state_predictions,
  get_eval_stats(
    true_prevalences = q66_male_true_prevalences,
    prevalence_preds = q66_male_prevalence_preds, 
    pred_method = "Previous year without other focal Q",
    pred_model = MODEL, 
    pred_predset = "Not Using Identity Responses",
    pred_year = 2015, 
    pred_col = "pred_prop_2017")$state_predictions
)

q66_male_real_prevs_states = unique(q66_male_state_preds[pred_method == "Same year without other focal Q", .(pred_state, real_prev, real_prev_lb, real_prev_ub)])
q66_male_real_prevs_states[, real_txt := paste0(
  format(real_prev*100,digits=0,nsmall=1), " (", 
  format(real_prev_lb*100,digits=0,nsmall=1), ", ", 
  format(real_prev_ub*100,digits=0,nsmall=1), ")")]
q66_male_real_prevs_states = q66_male_real_prevs_states[, .(pred_state, real_txt)]
#display(q66_real_prevs_states)

q66_male_pred_prevs_states = q66_male_state_preds[, .(pred_state, norm_oob_pe, norm_oob_lb, norm_oob_ub, pred_method)]
q66_male_pred_prevs_states[, pred_txt := paste0(
  format(norm_oob_pe*100,digits=0,nsmall=1), " (", 
  format(norm_oob_lb*100,digits=0,nsmall=1), ", ", 
  format(norm_oob_ub*100,digits=0,nsmall=1), ")")]
q66_male_pred_prevs_states_cast = dcast(q66_male_pred_prevs_states, pred_state ~ pred_method, value.var=c('pred_txt'))
#display(q66_pred_prevs_states_cast)

q66_male_merged = merge(q66_male_real_prevs_states, q66_male_pred_prevs_states_cast, by='pred_state')
q66_male_merged[is.na(q66_male_merged)] = ""
q66_male_merged = q66_male_merged[,.(
    pred_state, real_txt, `Same year with other focal Q`, `Same year without other focal Q`, `Previous year without other focal Q`
)]
fwrite(unique(q66_male_state_preds[, .(pred_state, real_prev)]), '~/YRBS_predictions/data/q66_male_real_prevs.csv')
fwrite(q66_male_merged, '~/YRBS_predictions/data/q66_male_merged_preds.csv')
fwrite(merge(q66_male_pred_prevs_states, unique(q66_male_state_preds[, .(pred_state, real_prev)]), by='pred_state'), '~/YRBS_predictions/data/q66_male_raw_preds.csv')
q66_male_merged
```
#### Evaluation summaries for each model type and prediction dataset (Q66)

```{r}
q66_all_model_summaries = rbind(
  rbindlist(lapply(q66_prevalence_preds[, unique(model)], function(m) {
    get_eval_stats(
    true_prevalences = q66_true_prevalences,
    prevalence_preds = q66_prevalence_preds, 
    pred_method = "Same year with other focal Q",
    pred_model = m, 
    pred_predset = "Using Identity Responses",
    pred_year = 2017, 
    pred_col = "pred_prop")$summary_stats
    })),
  rbindlist(lapply(q66_prevalence_preds[, unique(model)], function(m) {
    get_eval_stats(
    true_prevalences = q66_true_prevalences,
    prevalence_preds = q66_prevalence_preds, 
    pred_method = "Same year without other focal Q",
    pred_model = m, 
    pred_predset = "Not Using Identity Responses",
    pred_year = 2017, 
    pred_col = "pred_prop")$summary_stats
    })),
  rbindlist(lapply(q66_prevalence_preds[, unique(model)], function(m) {
    get_eval_stats(
    true_prevalences = q66_true_prevalences,
    prevalence_preds = q66_prevalence_preds, 
    pred_method = "Previous year without other focal Q",
    pred_model = m, 
    pred_predset = "Not Using Identity Responses",
    pred_year = 2015, 
    pred_col = "pred_prop_2017")$summary_stats
    }))
)

q66_long_version = q66_all_model_summaries[,.(
    pred_method, pred_model,
    label = paste0("ICC: ", oob_icc, " (p-val: ", oob_icc_pval,"); Coverage: ", round(oob_coverage,2)))]

q66_long_version[, pred_model := factor(pred_model, levels = c("ols", "logit", "lasso", "lassolog", "ridge", "ridgelog", "rf", "gbrt"))]
q66_long_version[, pred_method := factor(pred_method, levels = c("Same year with other focal Q", "Same year without other focal Q", "Previous year without other focal Q"))]

dcast(q66_long_version, pred_model ~ pred_method, value.var = "label")
```

#### Evaluation summaries for each model type and prediction dataset (Q67)

```{r}
q67_all_model_summaries = rbind(
  rbindlist(lapply(q67_prevalence_preds[, unique(model)], function(m) {
    get_eval_stats(
    true_prevalences = q67_true_prevalences,
    prevalence_preds = q67_prevalence_preds, 
    pred_method = "Same year with other focal Q",
    pred_model = m, 
    pred_predset = "Using Contact Responses",
    pred_year = 2017, 
    pred_col = "pred_prop")$summary_stats
    })),
  rbindlist(lapply(q67_prevalence_preds[, unique(model)], function(m) {
    get_eval_stats(
    true_prevalences = q67_true_prevalences,
    prevalence_preds = q67_prevalence_preds, 
    pred_method = "Same year without other focal Q",
    pred_model = m, 
    pred_predset = "Not Using Contact Responses",
    pred_year = 2017, 
    pred_col = "pred_prop")$summary_stats
    })),
  rbindlist(lapply(q67_prevalence_preds[, unique(model)], function(m) {
    get_eval_stats(
    true_prevalences = q67_true_prevalences,
    prevalence_preds = q67_prevalence_preds, 
    pred_method = "Previous year without other focal Q",
    pred_model = m, 
    pred_predset = "Not Using Contact Responses",
    pred_year = 2015, 
    pred_col = "pred_prop_2017")$summary_stats
    }))
)

q67_long_version = q67_all_model_summaries[,.(
    pred_method, pred_model,
    label = paste0("ICC: ", oob_icc, " (p-val: ", oob_icc_pval,"); Coverage: ", round(oob_coverage,2)))]

q67_long_version[, pred_model := factor(pred_model, levels = c("ols", "logit", "lasso", "lassolog", "ridge", "ridgelog", "rf", "gbrt"))]
q67_long_version[, pred_method := factor(pred_method, levels = c("Same year with other focal Q", "Same year without other focal Q", "Previous year without other focal Q"))]

dcast(q67_long_version, pred_model ~ pred_method, value.var = "label")
```


#### Evaluation summaries for each model type and prediction dataset (Q66 male)

```{r}
q66_male_all_model_summaries = rbind(
  rbindlist(lapply(q66_male_prevalence_preds[, unique(model)], function(m) {
    get_eval_stats(
    true_prevalences = q66_male_true_prevalences,
    prevalence_preds = q66_male_prevalence_preds, 
    pred_method = "Same year with other focal Q",
    pred_model = m, 
    pred_predset = "Using Identity Responses",
    pred_year = 2017, 
    pred_col = "pred_prop")$summary_stats
    })),
  rbindlist(lapply(q66_male_prevalence_preds[, unique(model)], function(m) {
    get_eval_stats(
    true_prevalences = q66_male_true_prevalences,
    prevalence_preds = q66_male_prevalence_preds, 
    pred_method = "Same year without other focal Q",
    pred_model = m, 
    pred_predset = "Not Using Identity Responses",
    pred_year = 2017, 
    pred_col = "pred_prop")$summary_stats
    })),
  rbindlist(lapply(q66_male_prevalence_preds[, unique(model)], function(m) {
    get_eval_stats(
    true_prevalences = q66_male_true_prevalences,
    prevalence_preds = q66_male_prevalence_preds, 
    pred_method = "Previous year without other focal Q",
    pred_model = m, 
    pred_predset = "Not Using Identity Responses",
    pred_year = 2015, 
    pred_col = "pred_prop_2017")$summary_stats
    }))
)

q66_male_long_version = q66_male_all_model_summaries[,.(
    pred_method, pred_model,
    label = paste0("ICC: ", oob_icc, " (p-val: ", oob_icc_pval,"); Coverage: ", round(oob_coverage,2)))]

q66_male_long_version[, pred_model := factor(pred_model, levels = c("ols", "logit", "lasso", "lassolog", "ridge", "ridgelog", "rf", "gbrt"))]
q66_male_long_version[, pred_method := factor(pred_method, levels = c("Same year with other focal Q", "Same year without other focal Q", "Previous year without other focal Q"))]

dcast(q66_male_long_version, pred_model ~ pred_method, value.var = "label")
```

#### Calculate LOO errors by prediction method for prediction intervals

```{r}
get_errors = function(q, true_prevalences, prevalence_preds, pred_method, pred_model, pred_predset, pred_year, pred_col) {
  
  subset_dt = prevalence_preds[
    model == pred_model &
    predset == pred_predset &
    year == pred_year
  ]

  pred_prev_by_state = subset_dt[,.(
    pred_state,
    pred_prev = get(pred_col),
    n
  )]

  pred_prev_by_state = merge(pred_prev_by_state, true_prevalences, by = 'pred_state')
  return(data.table(
    q = q,
    pred_method = pred_method, 
    pred_model = pred_model,
    pred_predset = pred_predset,
    oob_mean_bias = pred_prev_by_state[, mean(real_prev - pred_prev)],
    oob_sd = pred_prev_by_state[, sd(real_prev - pred_prev)],
    t_dist_df = pred_prev_by_state[, .N]-1))
}

error_dt = rbind(
  get_errors(
    q = "q67",
    true_prevalences = q67_true_prevalences,
    prevalence_preds = q67_prevalence_preds, 
    pred_method = "Same year with other focal Q",
    pred_model = "rf", 
    pred_predset = "Using Contact Responses",
    pred_year = 2017, 
    pred_col = "pred_prop"),
  get_errors(
    q = "q67",
    true_prevalences = q67_true_prevalences,
    prevalence_preds = q67_prevalence_preds, 
    pred_method = "Same year without other focal Q",
    pred_model = "rf", 
    pred_predset = "Not Using Contact Responses",
    pred_year = 2017, 
    pred_col = "pred_prop"),
  get_errors(
    q = "q67",
    true_prevalences = q67_true_prevalences,
    prevalence_preds = q67_prevalence_preds, 
    pred_method = "Previous year without other focal Q",
    pred_model = "rf", 
    pred_predset = "Not Using Contact Responses",
    pred_year = 2015, 
    pred_col = "pred_prop_2017"),
  get_errors(
    q = "q66",
    true_prevalences = q66_true_prevalences,
    prevalence_preds = q66_prevalence_preds, 
    pred_method = "Same year with other focal Q",
    pred_model = "rf", 
    pred_predset = "Using Identity Responses",
    pred_year = 2017, 
    pred_col = "pred_prop"),
  get_errors(
    q = "q66",
    true_prevalences = q66_true_prevalences,
    prevalence_preds = q66_prevalence_preds, 
    pred_method = "Same year without other focal Q",
    pred_model = "rf", 
    pred_predset = "Not Using Identity Responses",
    pred_year = 2017, 
    pred_col = "pred_prop"),
  get_errors(
    q = "q66",
    true_prevalences = q66_true_prevalences,
    prevalence_preds = q66_prevalence_preds, 
    pred_method = "Previous year without other focal Q",
    pred_model = "rf", 
    pred_predset = "Not Using Identity Responses",
    pred_year = 2015, 
    pred_col = "pred_prop_2017"),
  get_errors(
    q = "q66_male",
    true_prevalences = q66_male_true_prevalences,
    prevalence_preds = q66_male_prevalence_preds, 
    pred_method = "Same year with other focal Q",
    pred_model = "rf", 
    pred_predset = "Using Identity Responses",
    pred_year = 2017, 
    pred_col = "pred_prop"),
  get_errors(
    q = "q66_male",
    true_prevalences = q66_male_true_prevalences,
    prevalence_preds = q66_male_prevalence_preds, 
    pred_method = "Same year without other focal Q",
    pred_model = "rf", 
    pred_predset = "Not Using Identity Responses",
    pred_year = 2017, 
    pred_col = "pred_prop"),
  get_errors(
    q = "q66_male",
    true_prevalences = q66_male_true_prevalences,
    prevalence_preds = q66_male_prevalence_preds, 
    pred_method = "Previous year without other focal Q",
    pred_model = "rf", 
    pred_predset = "Not Using Identity Responses",
    pred_year = 2015, 
    pred_col = "pred_prop_2017")
)

fwrite(error_dt, '~/YRBS_predictions/data/error_dt.csv')

error_dt
```

# Visualization of a specific model and question

```{r, fig.width=14}
vis_dt_rf_q66 = rbind(
  get_eval_stats(
    true_prevalences = q66_true_prevalences,
    prevalence_preds = q66_prevalence_preds, 
    pred_method = "Same year with other focal Q",
    pred_predset = "Using Identity Responses",
    pred_year = 2017, 
    pred_model = "rf",
    pred_col = "pred_prop")$state_predictions,
  get_eval_stats(
    true_prevalences = q66_true_prevalences,
    prevalence_preds = q66_prevalence_preds, 
    pred_method = "Same year without other focal Q",
    pred_predset = "Not Using Identity Responses",
    pred_year = 2017,
    pred_model = "rf", 
    pred_col = "pred_prop")$state_predictions,
  get_eval_stats(
    true_prevalences = q66_true_prevalences,
    prevalence_preds = q66_prevalence_preds, 
    pred_method = "Previous year without other focal Q",
    pred_predset = "Not Using Identity Responses",
    pred_year = 2015,
    pred_model = "rf", 
    pred_col = "pred_prop")$state_predictions)

vis_dt_rf_q66_summmary_stats = rbind(
  get_eval_stats(
    true_prevalences = q66_true_prevalences,
    prevalence_preds = q66_prevalence_preds, 
    pred_method = "Same year with other focal Q",
    pred_predset = "Using Identity Responses",
    pred_year = 2017,
    pred_model = "rf", 
    pred_col = "pred_prop")$summary_stats,
  get_eval_stats(
    true_prevalences = q66_true_prevalences,
    prevalence_preds = q66_prevalence_preds, 
    pred_method = "Same year without other focal Q",
    pred_predset = "Not Using Identity Responses",
    pred_year = 2017,
    pred_model = "rf", 
    pred_col = "pred_prop")$summary_stats,
  get_eval_stats(
    true_prevalences = q66_true_prevalences,
    prevalence_preds = q66_prevalence_preds, 
    pred_method = "Previous year without other focal Q",
    pred_predset = "Not Using Identity Responses",
    pred_year = 2015,
    pred_model = "rf", 
    pred_col = "pred_prop")$summary_stats)

vis_dt_rf_q66_summmary_stats[, `:=`(
  label = paste0("ICC: ", oob_icc, " (p-val: ", oob_icc_pval,"; coverage: ", round(oob_coverage,2), ")"),
  x = vis_dt_rf_q66[,min(real_prev)],
  y = vis_dt_rf_q66[,max(norm_oob_pe)]
  )]
  

ggplot(vis_dt_rf_q66, aes(x=real_prev, ymin=norm_oob_lb, y=norm_oob_pe, ymax=norm_oob_ub, label=pred_state)) + 
  geom_pointrange() + geom_abline(intercept=0, slope=1, linetype = "dashed") + facet_wrap(~pred_method, ncol=2) + theme_bw() + 
  geom_label(size=3, color = "black", label.padding = unit(0.15, "lines")) +
  geom_label(data=vis_dt_rf_q66_summmary_stats, aes(label=label, x=x, y=y, fill=oob_icc), 
             vjust=0, hjust=0, inherit.aes=FALSE, color = "white", size=5) +
  ggtitle("Predicting Prevalence of Same-Sex Contact given Any Contact (Random Forest)") +
  xlab("True YRBS Point Estimate") +
  ylab("Prediction Interval") +
  theme(strip.text=element_text(size=14)) +
  theme(plot.title=element_text(hjust=0, size=18)) +
  theme(axis.text=element_text(size=14),
        axis.title=element_text(size=14)) +
  guides(fill=FALSE)
```

